### 2024-09-14 Response/Response.tex

The EN randomly selects a sample collection of experiences from the replay buffer, denoted as $\mathcal{N}$. For each experience $n \in \mathcal{N}$, it calculates the value of $	\hat{Q}^{\text{T}}_{i,n}$. This value represents the QoE in experience $n$ and includes a discounted Q-value of the action anticipated to be taken in the subsequent state of experience $n$, according to the network $\textit{Net}^\text{T}_i$, given by
\begin{alignat}{1}
	\hat{Q}_{i,n}^{\text{T}} = \boldsymbol{q}_i(n) + \gamma Q_i^{\text{T}}(\boldsymbol{s}_i(n+1)), \tilde{\boldsymbol{a}}_n; \theta_i^{\text{T}}),
	\label{28}  
\end{alignat}  
where $\tilde{\boldsymbol{a}}_n$ denotes the optimal action for the state $\boldsymbol{s}_i(n+1)$ based on its highest Q-value under $\textit{Net}_i^{\text{E}}$, as given by:
\begin{alignat}{1}
	\tilde{\boldsymbol{a}}_n = \text{arg} \; \max_{\boldsymbol{a} \in \mathcal{A}} \; Q_i^{\text{E}}(\boldsymbol{s}_i(n+1), \boldsymbol{a}; \theta_i^{\text{E}}).
	\label{29}  
\end{alignat} 
In particular, regarding experience $n$, the target-Q value $\hat{Q}_{i,n}^{\text{T}}$ represents the long-term QoE for action $\boldsymbol{a}_i(n)$ under state $\boldsymbol{s}_i(n)$. This value corresponds to the QoE observed in experience $n$, as well as the approximate expected upcoming QoE. %based on $\textit{Net}_i^{\text{T}}_i$, i.e., $\gamma Q_i^{\text{T}}(\mathcal{S}_i(i+1)), \mathcal{A}_i^{\text{N}}; \theta_i^{\text{T}})$
Based on the set $\mathcal{N}$, the EN trains the MD's neural network using previous sample experiences. Simultaneously, it updates $\theta^{\text{E}}_i$ in $\textit{Net}_i^{\text{E}}$ and computes vector $\hat{\mathbf{Q}}_i^{\text{T}} = (\hat{Q}^{\text{T}}_{i,n})_{n \in \mathcal{N}}$. The key idea of updating $\textit{Net}_i^{\text{E}}$ is to minimize the disparity in Q-values between $\textit{Net}_i^{\text{E}}$ and $\textit{Net}_i^{\text{T}}$, as indicated by the following loss function:
\begin{alignat}{1}
	\hspace{-2mm}L(\theta_i^{\text{E}},\hat{\mathbf{Q}}_i^{\text{T}}) = {1 \over |\mathcal{N}| }\hspace{-1mm} \sum\limits_{n \in \mathcal{N}} \bigg(Q_i^{\text{E}}(\boldsymbol{s}_i(n) , \boldsymbol{a}_i(n); \theta_i^{\text{E}} ) -   \hat{Q}^{\text{T}}_{i,n}  \bigg)^2.
	\label{30}  
\end{alignat}  
In every \textit{ReplaceThreshold} iterations, the update of $\textit{Net}_i^{\text{T}}$ will involve duplicating the parameters from $\textit{Net}_i^{\text{E}}$ ($\theta_i^{T} = \theta_i^{E}$). The objective is to consistently update the network parameter $\theta_i^{T}$ in $\textit{Net}_i^{\text{T}}$, which enhances the approximation of the long-term QoE when computing the target Q-values in \eqref{28}.\\

\subsubsection{Computational Complexity}

The computational complexity of the QECO algorithm is determined by the number of experiences required to discover the optimal offloading policy. Each experience involves backpropagation for training, which has a computational complexity of $\mathcal{O}(C)$, where $C$ represents the number of multiplication operations in the neural network. During each training round triggered by the arrival of a new task, a sample collection of experiences of size $|\mathcal{N}|$ is utilized from the replay buffer. Since the training process encompasses $N^{\text{ep}}$ episodes and there are $K$ expected tasks in each episode, the computational complexity of the proposed algorithm is $\mathcal{O}(N^{\text{ep}}K|\mathcal{N}|C$), which is polynomial. Given the integration of neural networks for function approximation, the convergence guarantee of the DRL algorithm remains an open problem. In this work, we will empirically evaluate the convergence of the proposed algorithm in Section \ref{section:2}.

%Regarding the convergence, as mentioned in many existing works (e.g., [29]), the convergence guarantee of a DRL algorithm is still an open problem. Despite the fact that the convergence of a reinforcement learning algorithm can be proven, a DRL algorithm requires function approximation (e.g., the approximation of the Q-values in deep Q-learning algorithm) using neural networks, under which the convergence may no longer be guaranteed. In this work, we empirically evaluate the convergence performance of the proposed algorithm in Section 5.1.

\section{Performance Evaluation}\label{section:V}
In this section, we first present the simulation setup and training configuration. We then illustrate the convergence of the proposed DRL-based QECO algorithm and evaluate its performance in comparison to three baseline schemes in addition to the existing work~\cite{yang2018distributed}.
%We begin by presenting the simulation setting and training configuration, followed by the evaluation of QECO algorithm under multiple key performance metrics in comparison to benchmark methods.

\subsection{Simulation Setup}
We consider a MEC environment with 50 MDs and 5 ENs, similar to \cite{9253665}. We also follow the model presented in \cite{zhou2021deep} to determine the energy consumption. All the parameters are given in Table~\ref{table}. To train the MDs' neural networks, we adopt a scenario comprising 1000 episodes. Each episode contains 100 time slots, each of length 0.1 second. The QECO algorithm incorporates real-time experience into its training process to continuously enhance the offloading strategy. Specifically, we employ a batch size of 16, maintain a fixed learning rate of 0.001, and set the discount factor $\gamma$ to 0.9. The probability of random exploration gradually decreases from an initial value 1, progressively approaching 0.01, all of which is facilitated by an RMSProp optimizer. %The convergence of the proposed algorithm is evaluated across a spectrum of neural network hyperparameters and algorithm configurations.

%In these simulations, we first evaluate the QECO algorithm for each of the influencing QoE factors, including the number of completed tasks, overall energy consumption, and average delay. Subsequently, we demonstrate the overall improvement of QECO in terms of average QoE by comparing it against the following benchmark methods across multiple challenging scenarios.
We use the following methods as benchmarks.
\begin{enumerate}

	\item \textbf{Local Computing (LC):} The MDs execute all of their computation tasks using their own computing capacity.

	\item \textbf{Full Offloading (FO):} Each MD dispatches all of its computation tasks while choosing the offloading target randomly. %It leverages their complete communication capacity and the computation resources allocated to them by the EN.

	\item \textbf{Random Decision (RD):} In this approach, when an MD receives a new task, it randomly makes the offloading decisions and selects the offloading target if it decides to dispatch the task. %This method leverages the MD's complete computational and communication capabilities, and the computational resources allocated to it by the EN.

	\item \textbf{PGOA~\cite{yang2018distributed}:} This existing method is a distributed optimization algorithm designed for delay-sensitive tasks in an environment where MDs interact strategically with multiple ENs. We select PGOA as a benchmark method due to its similarity to our work.
\end{enumerate}

%In this part, we first illustrate the convergence performance of the proposed DRL-based QECO algorithm, and then we compare its performance of these two proposed methods with the fiducial methods in terms of the energy con- sumption of the system and the average delay of the task at each time slot.

%In the following, we first show the convergence of the proposed algorithm across episodes. Then, we compare the performance of our proposed algorithm with the benchmark methods under different parameter settings.

%In the following, we will compare the performance of the QECO algorithm with benchmark methods under two different computation workloads. This comparison will involve increasing the task arrival rate and the number of MDs.

%\newpage

\begin{table}
	\centering
	\renewcommand{\arraystretch}{1}
	\captionsetup{name=TABLE}
	\caption{Simulation Parameters}
	\scalebox{1}{%
		\begin{tabular}{ l|l } 
			%\toprule
			\textbf{Parameter} & \textbf{Value}  \\ \hline
			%\midrule
			%Number of MDs $i$  & 50  \\ 
			%Number of EN $j$  & 5  \\ 
			%Number of episodes $N^{\text{ep}}$  & 1000  \\ 
			%Number of time slots $T$  & 100 (with $\tau = 0.1$ second) \\ 
			Computation capacity of MD $f_i$  & 2.6 GHz \\ 
			Computation capacity of EN $f_j^{\text{E}}$ & 42.8 GHz  \\ 
			Transmission capacity of MD $r_{i,j}(t)$ & 14 Mbps  \\ 
			Task arrival rate & 150 Task/sec  \\ 
			Size of task $\lambda_i(t)$  & $\{\text{1.0, 1.1, \ldots , 7.0}\}$ Mbits \\ 
			Required CPU cycles of task $\rho_i(t)$  & $\{\text{0.197,0.297,0.397}\}$ $\times10^3$ \\ 
			Deadline of task $ \Delta_i$  & 10 time slots (1 Sec)\\ 
			Battery level percentage of MD $\phi_i(t)$  & $\{\text{25, 50, 75}\}$\\ %Percent \\ 
			%Computation power of MD $p_i^{\text{C}}$ & \text{$10^{-27}(f_i)^3$}  \\ 
			Computation power of EN $p_j^{\text{E}}$ & 5 W  \\ 
			Transmission power of MD $p_i^{\text{T}}$ & 2.3 W  \\ 
			Standby power of MD $p_i^{\text{I}}$& 0.1 W  \vspace{1mm}\\ 
			%\toprule
	\end{tabular}}
	\label{table}
\end{table}

\subsection{Performance Comparison and Convergence}
\label{section:2}

%We evaluate the convergence of the proposed algorithm under different neural network hyperparameters and algorithm settings.

%We first investigate the effects of different hyper-parameters on the convergence performance of the proposed QECO algorithm, which is shown through the average QoE across episodes. In Fig. \ref{chart0} (a) the convergence of the proposed algorithm under different values of learning rate is shown, where the learning rate controls the step size in each iteration for moving towards the minimum of the loss function. %It can be observed that the average QoE in each episode increases rapidly as the training episodes increase, and the efficient computation offloading policies can be successfully learned as the interaction continues.
% In Fig. \ref{chart0} (a), learning rate = 0.001 leads to a relatively fast convergence and small converged cost. When the learning rate is small (i.e., 0.0001), the convergence is slow and the converged cost increases and also a too big learning rate cause poor convergence performance. Fig. \ref{chart0} (b) shows the convergence performance under different value of batch sizes, which refers to the number of sampled experiences in each training round. We vary the value of batch size of each MD from 4 to 16, batch size as 16 has the best convergence performance. As it further increases, the performance of the proposed algorithm does not have a significant improvement in terms of the convergence speed and the converged result. We set the default values of batch size for each MD as 16.

%Fig. 4 (b) shows the algorithm performance under differ- ent batch sizes, i.e., the number of experiences sampled in each training round. As the batch size increases from 2 to 8, the convergence speed increases. As it further increases from 8 to 32, the performance of the proposed algorithm does not have a significant improvement in terms of the convergence speed and the converged result. Thus, we can choose a small batch size (e.g., 8) to reduce the time for one round of training without significantly reducing the performance of the proposed algorithm.

%lr = 10 3 leads to a relatively fast convergence and small converged cost.

%Based on the parameters given in Table \ref{table}, the learning process commences with random policy, and after about 400 episodes, the proposed algorithm achieves an average QoE of 0.77.

%We first delve into the investigation of the convergence performance of the proposed QECO algorithm, which is shown through the average QoE across episodes in Fig. \ref{chart0} (a).

%This represents a notable enhancement of 77\% and 16\% over LC and PGOA, respectively. This improvement is attributed to our algorithm's ability to reduce each user-associated cost regarding \eqref{28}, while striving to increase the number of completed tasks. As shown in Figs. \ref{chart0} (b), the converged QECO algorithm decreases the average cost by 38\% compared to RD and 25\% compared to PGOA.

%\subsection{Method Comparison}
%In this part, we first investigate the performance of the proposed DRL-based algorithm under different computation workloads in comparison to benchmark methods across several key performance metrics, including the number of completed tasks, average delay, and energy consumption in the entire system. Then, we evaluate the average QoE of users, which is a balance among these metrics with meticulous attention to users' demands.

We first evaluate the number of completed tasks when comparing our proposed QECO algorithm with the other four schemes. As illustrated in Fig.~\ref{chart1} (a), the QECO algorithm consistently outperforms the benchmark methods when we vary the task arrival rate. At a lower task arrival rate (i.e., 50), most of the methods demonstrate similar proficiency in completing tasks. However, as the task arrival rate increases, the efficiency of QECO becomes more evident. Specifically, when the task arrival rate increases to 250, our algorithm can increase the number of completed tasks by 73\% and 47\% compared to RD and PGOA, respectively.
Similarly, in Fig.~\ref{chart1} (b), as the number of MDs increases, QECO shows significant improvements in the number of completed tasks compared to other methods, especially when faced with a large number of MDs. When there are 110 MDs, our proposed algorithm can effectively increase the number of completed tasks by at least 34\% comparing with other methods. This achievement is attributed to the QECO's ability to effectively handle unknown workloads and prevent congestion at the ENs.

Figs.~\ref{chart2} (a) and ~\ref{chart2} (b) illustrate the overall energy consumption for different values of task arrival rate and the number of MDs, respectively. At the lower task arrival rate, the total energy consumption of all methods is close to each other. The total energy consumption increases when we have a higher task arrival rate.  
%When the task arrival rate increases, the total energy consumption of each method increases differently. It can be found that the production of more computational tasks leads to a continuous increase in energy consumption until the capacity is saturated, and the energy consumption remains constant at its maximum. The QECO algorithm takes into account the battery level of the MD in its decision-making process. 
As can be observed from Fig.~\ref{chart2} (a), at task arrival rate 450, QECO effectively reduces overall energy consumption by 18\% and 15\% compared to RD and PGOA, respectively, as it takes into account the battery level of the MD in its decision-making process. However, it consumes more energy compared to LC and FO because they do not utilize all computing resources. In particular, LC only uses the MD's computational resources, while FO utilizes the allocated EN computing resources.

\begin{figure}[tbp]
	\centering
	\captionsetup{name=Fig.}
	\begin{minipage}[b]{0.34\linewidth}
		\centering
		\includegraphics[width=\textwidth]{Fig/completed_tasks_1} 
		\textcolor{white}{i}\hspace{0.6cm}(a)
	\end{minipage}
	\hspace{-0.2cm}
	\begin{minipage}[b]{0.34\linewidth}
		\centering
		\includegraphics[width=\textwidth]{Fig/completed_tasks_2}
		\textcolor{white}{i}\hspace{0.6cm}(b)
	\end{minipage}
	%\vspace{-0.65cm}
	\caption{The number of completed tasks under different computation workloads: (a) task arrival rate; (b) the number of MDs.}
	\label{chart1}
\end{figure}

\begin{figure}[tbp]
	\centering
	\captionsetup{name=Fig.}
	\begin{minipage}[b]{0.340\linewidth}
		\centering
		\includegraphics[width=\textwidth]{Fig/energy_1} 		
		\textcolor{white}{i}\hspace{0.6cm}(a)
	\end{minipage}
	%\hspace{-0.2cm}
	\begin{minipage}[b]{0.340\linewidth}
		\centering
		\includegraphics[width=\textwidth]{Fig/energy_2}
		\textcolor{white}{i}\hspace{0.6cm}(b)
	\end{minipage}
	%\vspace{-0.7cm}
	\caption{The overall energy consumption under different computation workloads: (a) task arrival rate; (b) the number of MDs.}
	\label{chart2}
\end{figure}

\begin{figure}[t]
	\centering
	\captionsetup{name=Fig.}
	\begin{minipage}[b]{0.340\linewidth}
		\centering
		\includegraphics[width=\textwidth]{Fig/delay_1} 		
		\textcolor{white}{i}\hspace{0.6cm}(a)
	\end{minipage}
	\hspace{-0.2cm}
	\begin{minipage}[b]{0.340\linewidth}
		\centering
		\includegraphics[width=\textwidth]{Fig/delay_2}
		\textcolor{white}{i}\hspace{0.6cm}(b)
	\end{minipage}
	%\vspace{-0.7cm}
	\caption{The average delay under different computation workloads: (a) task arrival rate; (b) the number of MDs.}
	\label{chart3}
\end{figure}

\begin{figure}[tbp]
	\centering
	\captionsetup{name=Fig.}
	\begin{minipage}[b]{0.340\linewidth}
		\centering
		\includegraphics[width=\textwidth]{Fig/qoe_1} 		
		\textcolor{white}{i}\hspace{0.6cm}(a)
	\end{minipage}
	\hspace{-0.2cm}
	\begin{minipage}[b]{0.340\linewidth}
		\includegraphics[width=\textwidth]{Fig/qoe_2}
		\textcolor{white}{i}\hspace{0.6cm}(b)
	\end{minipage}
	%\vspace{-0.7cm}
	\caption{The average QoE under different computation workloads: (a) task arrival rate; (b) the number of MDs.}
	\label{chart4}
\end{figure}

In Fig.~\ref{chart2} (b), an increasing trend in overall energy consumption is observed as the number of MDs increases since the number of resources available in the system increases, which leads to higher energy consumption. The QECO algorithm consistently outperforms RD and PGOA methods in overall energy consumption, especially when there are a large number of MDs. Specifically, QECO demonstrates a 27\% and 16\% reduction in overall energy consumption compared to RD and PGOA, respectively, when the number of MDs increases to 110.

As shown in Fig.~\ref{chart3} (a), the QECO algorithm maintains a lower average delay compared to other methods as the task arrival rate increases from 50 to 350. Specifically, when the task arrival rate is 200, it reduces the average delay by at least 12\% compared to other methods. However, for task arrival rates exceeding 350, QECO may experience a higher average delay compared to some of the other methods. This can be attributed to the fact that the other algorithms drop more tasks while our proposed algorithm is capable of completing a higher number of tasks, potentially leading to an increase in average delay. In Fig.~\ref{chart3} (b), as the number of MDs increases, we observe a rising trend in the average delay. It can be inferred that an increase in computational load in the system can lead to higher queuing delays and computations at ENs. Considering the QECO's ability to schedule workloads, when the number of MDs increases from 30 to 110, it consistently maintains a lower average delay which is at least 8\% less than the other methods.

### 2024-09-14 Response/Response.tex

%Fig. 6 illustrates a performance comparison of methods in terms of energy consumption in the entire system, considering an increase in the task arrival rate and the number of MDs. With efficient decision-making, the DRL-based algorithm achieves lower energy consumption in both cases compared to RD and PGOA. However, it consumes more energy compared to LC and FC. This is because LC only utilizes the MD's computational resources, and FC solely utilizes the transmission link. In Fig. 6(a), when the task arrival rate is low, the energy consumption of all methods is close to each other, and as the task arrival rate increases, the energy consumption of each method also increases. It can be observed that the generation of more computational tasks leads to a continuous increase in energy consumption. When the task arrival rate increases from 0.1 to 0.9, the DRL-based algorithm increases by 20\%, while RD and PGOA increase by at least 30\%. Similarly, in Fig. 6(b), the DRL-based algorithm effectively reduces energy consumption, especially when the number of MDs is large.The DRL-based algorithm demonstrates a 15\% reduction in energy consumption compared to RD and a 30\% reduction compared to PGOA as the number of MDs increases to 110.

%In the following, we delve into the investigation of the overall improvement achieved by the QECO algorithm in comparison to other methods in terms of the average QoE as the task arrival rate and the number of MDs increase. This metric signifies the average advantage created by each method for MDs, including a combination of the values of the previously evaluated metrics (task completion, delay, energy consumption) according to the demands of MDs.

%The average QoE comparison in Fig.~\ref{chart4} (a) indicates the superiority of the QECO algorithm in providing MDs with a better experience. By taking into account the specific demands of MDs for each key performance metric, it consistently achieves a higher average QoE across various values of arrival task rates when compared to other methods. Specifically, when the task arrival rate is moderate (i.e., 250), QECO increases the average QoE by 57\% and 33\% compared to RD and PGOA, respectively. In Fig.~\ref{chart4} (b), As the number of MDs increases, the potential workload on the ENs also rises, leading to a decrease in the average QoE for each method (excluding LC). It can be observed that an increase in the ENs' workload leads to a reduction in the allocated computing capacity for MDs, resulting in a decrease in the average QoE. However, QECO effectively manages the uncertain load at the ENs. When the number of MDs increases to 90, it increases the average QoE by at least 29\% more than the other methods.

We further investigate the overall improvement achieved by the QECO algorithm in comparison to other methods in terms of the average QoE. This metric signifies the advantages MDs obtain by utilizing different algorithms. Fig.~\ref{chart4} (a) shows the average QoE for different values of task arrival rate. This figure indicates the superiority of the QECO algorithm in providing MDs with an enhanced experience. Specifically, when the task arrival rate is moderate (i.e., 250), QECO improves the average QoE by 57\% and 33\% compared to RD and PGOA, respectively. Fig.~\ref{chart4} (b) illustrates the average QoE when we increase the number of MDs. The EN's workload grows when there are a larger number of MDs, leading to a reduction in the average QoE of all methods except LC. However, QECO effectively manages the uncertain load at the ENs. When the number of MDs increases to 90, QECO achieves at least a 29\% higher QoE comparing with the other methods.
It is worth noting that although improvements in each of the QoE factors can contribute to enhancing system performance, it is essential to consider the user's demands in each time slot. Therefore, the key difference between QECO and other methods is that it prioritizes users' demands, enabling it to strike an appropriate balance among them, ultimately leading to a higher QoE for MDs.

We finally delve into the investigation of the convergence performance of the QECO algorithm, which is shown through the average QoE across episodes in Figs.~\ref{chart0} (a) and~\ref{chart0} (b). We explore the impact of two main hyper-parameters on the convergence speed and the converged result of the proposed algorithm. Fig. \ref{chart0} (a) illustrates the convergence of the proposed algorithm under different learning rates, where the learning rate regulates the step size per iteration towards minimizing the loss function. The QECO algorithm achieves an average QoE of 0.77 after around 400 episodes when the learning rate is 0.001, indicating relatively rapid convergence. However, with smaller learning rates (e.g., 0.0001) or larger values (e.g., 0.01),  a slower convergence is observed. Fig. \ref{chart0} (b) shows the convergence of the proposed algorithm under different batch sizes, which refer to the number of sampled experiences in each training round. An improvement in convergence performance is observed as the batch size increases from 4 to 16. However, further increasing the batch size from 16 to 32 does not notably enhance the converged QoE or convergence speed. Hence, a batch size of 16 may be more appropriate for training processes.

\begin{figure}
	\centering
	\captionsetup{name=Fig.}
	\begin{minipage}[b]{0.34\linewidth}
		\centering
		\includegraphics[width=\textwidth]{Fig/conv1_f} 
		\textcolor{white}{i}\hspace{0.4cm}(a)
	\end{minipage}
	\hspace{-0.26cm}
	\begin{minipage}[b]{0.4\linewidth}
		\centering
		\includegraphics[width=\textwidth]{Fig/conv2_f}
		\textcolor{white}{i}\hspace{0.4cm}(b)
	\end{minipage}
	\vspace{-0.65cm}
	\caption{The convergence of the average QoE across episodes under different hyper-parameters: (a) Learning rate; (b) Batch size.}
	\label{chart0}
\end{figure}

\section{Conclusion}\label{section:VI}
%In this study, our focus was directed towards addressing the challenge of offloading in MEC systems, where strict task processing deadlines and energy constraints adversely impact system performance. To address this challenge, we propose the QECO algorithm specifically designed to empower MDs to make offloading decisions without relying on knowledge about task models or other MDs' offloading decisions. The QECO algorithm not only adapts to the uncertain dynamics of load levels at ENs but also effectively manages the ever-changing system environment. Through extensive simulations, we demonstrate that QECO outperforms several established benchmark techniques. Specifically, it can significantly increase the average user's QoE. This advantage can lead to improvements in key performance metrics, including task completion rate, task delay, and energy consumption, according to the user's demands under different system conditions.

%There are multiple directions for extend this research. A complementary approach involves extending the simplified task model by considering dependent divisible tasks that correspond to actual computational tasks. This can be achieved by incorporating a call graph~\cite{kwok1996dynamic} representation to develop relationships among task partitions. Furthermore, in order to accelerate the learning of optimal offloading policies, it is beneficial to enable MDs to take advantage of federated learning~\cite{li2020federated} techniques in the training process. This allows MDs to collectively contribute to improving the offloading model and enables continuous learning when new MDs join the network.

In this paper, we focused on addressing the challenge of offloading in MEC systems, where strict task processing deadlines and energy constraints adversely impact system performance. We formulated an optimization problem that aims to maximize the QoE of each MD individually, while QoE reflects the energy consumption and task completion delay. To address the dynamic and uncertain mobile environment, we proposed a QoE-oriented DRL-based computation offloading algorithm called QECO. Our proposed algorithm empowers MDs to make offloading decisions without relying on knowledge about task models or other MDs' offloading decisions. The QECO algorithm not only adapts to the uncertain dynamics of load levels at ENs, but also effectively manages the ever-changing system environment. Through extensive simulations, we showed that QECO outperforms several established benchmark techniques, while demonstrating a rapid training convergence. Specifically, QECO increases the average user's QoE by 37\% compared to an existing work. This advantage can lead to improvements in key performance metrics, including task completion rate, task delay, and energy consumption, under different system conditions and varying user demands.

There are multiple directions for future work. A complementary approach involves extending the task model by considering interdependencies among tasks. This can be achieved by incorporating a task call graph representation. Furthermore, in order to accelerate the learning of optimal offloading policies, it will be beneficial to take advantages of federated learning techniques in the training process. This will allow MDs to collectively contribute to improving the offloading model and enable continuous learning when new MDs join the network.

\newpage

\begin{abstract}
	Mobile edge computing (MEC) is envisioned to address the computation demands of Internet of Things (IoT) devices. However, it is crucial for the MEC to operate in coordination with the cloud tier to achieve a highly scalable IoT system. In addition, IoT devices require regular maintenance to either recharge or replace their batteries which may not always be feasible. Wireless energy transfer (WET) can provide IoT devices a stable source of energy. Nonetheless, proper scheduling of energy harvesting and efficient allocation of computing resources are the key for sustainable operation of these devices. In this paper, we introduce a three-tier wireless powered mobile edge computing (WPMEC) consisting of cloud, MEC servers, and IoT devices. We first formulate a combinatorial optimization problem that aims to minimize the wireless energy transmission. To tackle the complexity of the problem, we use bipartite graph matching and propose a harvest-then-offload mechanism for IoT devices. We also exploit parallel processing to increase the performance of the proposed algorithm. Through numerical experiments, we evaluate the performance of our proposed mechanism. Our results show that the proposed mechanism significantly reduces the required energy for the operation of IoT devices comparing to different offloading policies. \textcolor{blue}{We further show that WiEnTM results in up to 34\% less wireless energy transmission in comparison to an existing work in the literature.}
\end{abstract}

\begin{IEEEkeywords}
	Bipartite graph matching, mobile edge computing (MEC), wireless power transfer (WPT), Internet of Things (IoT)
\end{IEEEkeywords}

\section{Introduction}
\textcolor{blue}{The Internet of Things (IoT) applications (e.g., smart cities \cite{b1}, homes \cite{b3}, and augmented/virtual reality \cite{b11}) are mostly involved with computation-intensive and latency-sensitive tasks. Mobile edge computing (MEC) is a state-of-the-art computation paradigm to address the challenge of insufficient computing resources in IoT networks \cite{b35, b4}. By deploying the edge servers, nearby devices can offload their computation tasks. Dispatching those tasks that require a higher amount of energy will let devices save more energy \cite{b38}. However, as the computation tasks become more and more intensive, coordination with cloud servers will be inevitable \cite{b37}. The three-tier computing models consisting of cloud, edge, and IoT devices are introduced to overcome the aforementioned challenge \cite{b5,b6,b39,b40}.}

\textcolor{blue}{In addition to their restricted computation resources, IoT devices usually have small battery capacities which is mainly due to their small form factor and the constraints of the production cost \cite{b1}.} Thus, their battery needs to be replaced or recharged quite often which may be infeasible or costly in some cases such as toxic \cite{b7} or hard-to-reach environments \cite{b4}. Thanks to the latest developments of radio frequency (RF) enabled wireless energy transfer (WET) technology, a promising solution called wireless powered communication (WPC) has been introduced \cite{b8}. In WPC, wireless devices (WDs) are powered by dedicated energy transmitters (ETs) \cite{b8}. As wireless powered networks do not require replacement or manual recharging of batteries, they have significantly lower maintenance costs. Therefore, these networks are more scalable compared to the battery powered networks in terms of size \cite{b8}. \textcolor{blue}{By combining the advantages of MEC and WPC, the newly emerged wireless powered MEC (WPMEC) holds a major promise to overcome the fundamental hurdles in scalability of the IoT networks \cite{b9,b10,b30,b33}.}

Computation offloading has attracted many research projects in recent years \cite{b5,b39,b40,b11,b13,b29,b26,b28,b32}. \textcolor{blue}{It helps WDs save more energy and reduce the tasks' execution time.} As energy is crucial for the operation and maintenance of wireless powered systems, many of these works are focusing on analyzing and optimizing energy. Aazam \textit{et al.} in \cite{b5} analyzed the energy and performance of a three-tier cloud-edge-IoT offloading model. \textcolor{blue}{In \cite{b39}, authors proposed a scheme that aims to minimize the total cost in terms of energy and delay for a three-tier cloud-edge-IoT system. Gao \textit{et al.} in \cite{b40} proposed an offloading algorithm to minimize an objective called the energy time cost for a three-tier network. Although \cite{b5}, \cite{b39}, and \cite{b40} all benefit from a computationally-scalable three-tier system, IoT devices still rely on battery energy and hence lack the sustainability feature of WPMEC systems.} In \cite{b11}, authors provided a method to maximize energy efficiency in a two-user WPMEC system with user cooperation, non-divisible tasks, and harvest-then-offload TDMA protocol. Wang \textit{et al.} in \cite{b13} presented a heuristic solution to reduce the ET's total transmission energy consumption over a finite horizon in a single-user WPMEC system. In \cite{b29}, authors presented a single-user WPMEC framework with task partitioning to jointly optimize the computation rate and transmit energy. The methods proposed in \cite{b11,b13,b29} are not suitable for larger networks. Zhang \textit{et al.} in \cite{b26} introduced a decentralized game for a multi-user MEC system to optimize the ET's energy and computation costs. Nonetheless, reaching an equilibrium may require a considerable number of iterations. It also needs all WDs to cooperate with each other which may not be feasible in many cases. Huang \textit{et. al} in \cite{b28} proposed an offloading algorithm based on deep reinforcement learning for WPMEC systems with non-divisible tasks to maximize a value function (e.g., computation rate or energy efficiency). \textcolor{blue}{However, the proposed system model is oversimplified and thus less applicable to real-world scenarios.} He \textit{et al.} in \cite{b32} designed a scheduling algorithm to minimize the processing energy consumption for a multi-user WPMEC network with multiple access points (APs) and non-divisible tasks. As a task usually models a program, it consists of a number of interrelated subprograms. It may also include subprograms to send and retrieve data which cannot be offloaded. Therefore, non-divisible task models used in \cite{b11,b26,b28}, and \cite{b32} may not accurately represent real world applications. Additionally, such models cannot properly utilize multiple computing resources.

By considering the challenges of the aforementioned works, the following questions arise:
\begin{enumerate}
	\item \textcolor{blue}{\textit{How can we take advantage of cloud computing in addition to MEC to meet different requirements of IoT applications?}}
	\item \textcolor{blue}{\textit{How can we provide RF energy to enable the battery-less IoT devices operate seamlessly?}}
	\item \textcolor{blue}{\textit{What would be the optimal offloading decision when considering the subtasks' interdependencies?}}
\end{enumerate}

To answer these questions, we propose a novel three-tier WPMEC system with multiple WDs to minimize the ET's total transmitted energy. In the proposed system, we partition tasks into a number of fine-grained subtasks to consider their interdependencies. We design an offloading and scheduling algorithm to be executed efficiently on parallel processors such as graphical processing units (GPUs). \textcolor{blue}{This significantly reduces the execution time of the algorithm.}

\begin{figure}
	\centering
	\includegraphics[width=.33\textwidth]{system_model.pdf}
	\caption{Proposed three-tier WPMEC system in an IoT network.}\label{fig1}
\end{figure}

Our main contributions are as follows.
\begin{enumerate}
	\item \textit{Problem formulation}: We formally define the mixed-integer ET's energy minimization (ETEM) problem by deciding on offloading, WET time, and computation scheduling of subtasks for a multi-user three-tier WPMEC system \textcolor{blue}{considering task interdependencies and MEC server computation time.}
	\item \textit{Algorithm design}: We propose wireless energy transmission minimization (WiEnTM) algorithm based on bipartite graph matching. We first study the properties of the problem to decompose it into individual problems for each subtask to make it suitable for the matching algorithm. \textcolor{blue}{By efficiently utilizing parallel processing on decomposed problems, we prove that our proposed algorithm has a logarithmic time complexity with respect to the network size.}
	\item \textit{Performance evaluation}: Extensive numerical experiments are carried out to evaluate the proposed algorithm. Our experiments show major reduction in the WDs' required energy in comparison with baseline offloading policies. \textcolor{blue}{The algorithm also reduces the energy consumption by 34\% for large tasks compared to an existing work \cite{b13}.}
\end{enumerate}

The rest of this paper is organized as follows. In Section II, we first present the MEC system model including the edge and cloud servers and IoT devices. We then present the computation task partitioning model. Section III consists of the energy optimization problem and a step-by-step formulation. In Section IV, we propose our WiEnTM algorithm to efficiently solve the problem. Simulation results are presented in Section V. We conclude the paper in Section VI.

\section{System Model}
In this section, we first introduce the IoT network and computation task models. The IoT network consists of IoT devices and computing servers. The task model represents the subtasks as a directed acyclic graph (DAG) and introduces its associated properties. \textcolor{blue}{Some of the key notations are listed in Table \ref{table1}}.

\subsection{Network Model}
As illustrated in Fig. \ref{fig1}, we consider a three-tier WPMEC system with a cloud server and a hybrid access point (HAP)\footnote{Our analysis can be extended to the case of multiple HAPs by modeling the MEC server as a pool of edge computing servers and considering the fact that each IoT device can only be connected to an HAP.} in a network of multiple WDs. \textcolor{blue}{The HAP is equipped with an MEC server and an ET. MEC and the cloud servers are both able to receive and execute the offloaded tasks and then send the results back to WDs.} ET broadcasts stable RF power to WDs. Thus, with proper scheduling, WDs can sustain their operation by only relying on the harvested energy \cite{b8}. In order to allow multiple WDs to share the same RF-channel, we assume a time-division multiple access (TDMA) protocol for WDs, as inspired by \cite{b11} and \cite{b14}. Moreover, we assume that WDs have half-duplex transmission. As a result, computation offloading cannot be performed simultaneously with energy harvesting \cite{b2}. We thus adopt the \textit{harvest-then-offload} \cite{b2} model of scheduling, as shown in Fig. \ref{fig2}. \textcolor{blue}{In contrast, for the case of full-duplex transmission, scheduling algorithms are categorized as the simultaneous wireless information and power transfer (SWIPT) \cite{b8} mode. However, considering the constraints of the production costs and devices' form factor for battery-less WDs, they usually lack a full-duplex transceiver for energy harvesting and data transmission.}
